---
title: "Measurement invariance and multigroup analysis with metis"
author: "Aaron Akuteye"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Measurement invariance and multigroup analysis with metis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
set.seed(1)
```

## Overview

`metis` runs the Measurement Invariance of Composite Models (MICOM) procedure of
Henseler, Ringle and Sarstedt (2016) for a fitted `seminr` model, and provides
wrappers for bootstrap PLS multigroup analysis. A two-group comparison of
structural paths is defensible only when at least partial measurement invariance
holds, so MICOM precedes multigroup analysis.

## A fitted model and a grouping variable

```{r, eval = requireNamespace("seminr", quietly = TRUE)}
library(metis)
library(seminr)

data <- mobi
data$group <- rep(c("A", "B"), length.out = nrow(data))

mm <- constructs(
  composite("Image",       multi_items("IMAG", 1:5)),
  composite("Expectation", multi_items("CUEX", 1:3)),
  composite("Quality",     multi_items("PERQ", 1:7))
)
sm <- relationships(
  paths(from = "Image",       to = "Expectation"),
  paths(from = "Expectation", to = "Quality")
)
model <- estimate_pls(data, mm, sm)
```

## Running MICOM

```{r, eval = requireNamespace("seminr", quietly = TRUE)}
mi <- metis_micom(model, data, group_var = "group", permutations = 500)
mi$step2
```

The result reports the permutation admissibility of Step 2 explicitly.

```{r, eval = requireNamespace("seminr", quietly = TRUE)}
mi$admissibility
mi$invariance$message
```

## Multigroup analysis, cautioned by MICOM

```{r, eval = requireNamespace("seminr", quietly = TRUE)}
mga <- metis_pls_mga(model, data, group_var = "group", nboot = 500,
                     micom_result = mi)
mga$paths
```

## Formative constructs

Regression weights (`mode_B`) give formative composites. The same MICOM call
applies without change.

```{r, eval = FALSE}
mm_formative <- constructs(
  composite("Image",       multi_items("IMAG", 1:5), weights = mode_B),
  composite("Expectation", multi_items("CUEX", 1:3), weights = mode_B)
)
```

## Validation

Step 2 and Step 3 results are cross-verified against `cSEM::testMICOM`. `cSEM` is
a validation dependency only and is never required at runtime.

## Reference

Henseler, J., Ringle, C. M., & Sarstedt, M. (2016). Testing measurement
invariance of composites using partial least squares. *International Marketing
Review*, 33(3), 405-431.
